---
title: "crime"
output: html_document
date: "2023-04-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
```{r}
library(tidyverse)
```


```{r}
## Data from the Porland Police Bureau- https://public.tableau.com/app/profile/portlandpolicebureau/viz/New_Monthly_Neighborhood/MonthlyOffenseTotals

## Metadata: https://www.portland.gov/police/open-data/crime-statistics#toc-metadata-for-offense-open-data

crime<- read.csv("https://raw.githubusercontent.com/karolo89/Raw_Data/main/CrimeData-2023.csv")%>%select(-Address)
head(crime)
```
```{r}
crime$Year <-  format(as.Date(crime$OccurDate, format="%m/%d/%Y"),"%Y")

crime$Month <- format(as.Date(crime$OccurDate, format="%m/%d/%Y"),"%m")

crime$weekday <- weekdays(as.Date(crime$OccurDate))

crime$weekdaynum <- recode(crime$weekday,
                        "Sunday"="0",
                        "Monday"= "1",
                        "Tuesday"= "2",
                        "Wednesday"="3",
                        "Thursday"= "4",
                        "Friday"="5",
                        "Saturday"="6")

crime <- crime %>%
    select(-c("OpenDataLat", "OpenDataLon", "OpenDataX", "OpenDataY", "ReportDate"))
```

```{r}
## Convert string to time format
crime$OccurTime<- format(substr(as.POSIXct(sprintf("%04.0f",crime$OccurTime), format='%H%M'), 12, 16))

crime$time <- as.numeric( sub("\\D*(\\d+).*", "\\1", crime$OccurTime))

head(crime)
```
```{r}
## Prepare data

day_week <- crime %>%
  filter(Year== 2023)%>% select(Year, weekdaynum, time, OffenseCategory) %>% 
  mutate(weekday= as.factor(weekdaynum))%>%
  mutate(OccurTime= as.factor(time))%>%
  group_by(time, weekday, OffenseCategory)%>%
    summarise(count = n()) %>%
    arrange(desc(count))%>%
  na.omit()


write_rds(day_week, file = './day_week.rds')
```

```{r}
## Graph- Year selection

day_weekp <- ggplot(day_week %>% filter(OffenseCategory == "Larceny Offenses")) +
  aes(x = weekday, y = time) +
  geom_tile(aes(fill=count), colour = "white") +
  scale_fill_distiller(name= "# Offenses", palette = "YlGnBu", direction = 1) +
  scale_x_discrete(breaks = c("0", "1", "2", "3", "4", "5", "6"),
                   label = c("Sunday", "Monday", "Tuesday", "Wednesday","Thursday", "Friday", "Saturday"), expand=c(0,0))+
  
  labs(title="Number of Cases Reported in Portland, OR during January & February 2023",
       x="", 
       y="Hour")+
  theme_classic()+
  
  theme(
      
    axis.line=element_blank(),                                               
    axis.ticks=element_line(size=0.4),
    axis.text = element_text(size= 10, color= "#1e1b25"),
    axis.line.x = element_line(color= "#1e1b25" ),
    
    plot.background=element_blank(),         
    plot.title = element_text(size =11, hjust = 0, color= "#1e1b25", face = "bold"),

    panel.grid = element_blank(),
    
    legend.position = "bottom",
    legend.title = element_text(size= 8),
    legend.margin=margin(grid::unit(0,"cm")),
    legend.key.width=grid::unit(2,"cm"),
    legend.key.height=grid::unit(0.2,"cm")
)+
  coord_flip() 
```

```{r}
day_weekp
```
```{r}
crime_list = list(unique(crime$OffenseType))
```
crimes[[1]] = filter(crime_time, OffenseCategory == crimes[[1]]),
                   crimes[[2]] = filter(crime_time, OffenseCategory == crimes[[2]]),
                   crimes[[3]] = filter(crime_time, OffenseCategory == crimes[[3]]),
                   crimes[[4]] = filter(crime_time, OffenseCategory == crimes[[4]]),
                   crimes[[5]] = filter(crime_time, OffenseCategory == crimes[[5]]),
                   crimes[[6]] = filter(crime_time, OffenseCategory == crimes[[6]]),
                   crimes[[7]] = filter(crime_time, OffenseCategory == crimes[[7]]),
                   crimes[[8]] = filter(crime_time, OffenseCategory == crimes[[8]]),
                   crimes[[9]] = filter(crime_time, OffenseCategory == crimes[[9]]),
                   crimes[[10]] = filter(crime_time, OffenseCategory == crimes[[10]]),
                   crimes[[11]] = filter(crime_time, OffenseCategory == crimes[[11]]),
                   crimes[[12]] = filter(crime_time, OffenseCategory == crimes[[12]]),
                   crimes[[13]] = filter(crime_time, OffenseCategory == crimes[[13]]),
                   crimes[[14]] = filter(crime_time, OffenseCategory == crimes[[14]]),
                   crimes[[15]] = filter(crime_time, OffenseCategory == crimes[[15]]),
                   crimes[[16]] = filter(crime_time, OffenseCategory == crimes[[16]]),
                   crimes[[17]] = filter(crime_time, OffenseCategory == crimes[[17]]),
                   crimes[[18]] = filter(crime_time, OffenseCategory == crimes[[18]]),                   
                   crimes[[19]] = filter(crime_time, OffenseCategory == crimes[[19]]),
                   crimes[[20]] = filter(crime_time, OffenseCategory == crimes[[20]])
